Synthetic Observations of Extremely High Velocity (EHV) SiO components in young molecular outflows

### 2014-01-22 PAPER/Paola_2/ms_ver3.tex
Modified fig captions I

\begin{figure*}
 \includegraphics[width=2.\columnwidth]{\figpath/pfig4.pdf}%{\figpath/diffcool_sim.pdf}
 \caption{Jet Volume Density for different cooling modes with
   $\eta$ = 10.}
\label{fig:coolcmpdyn}
\end{figure*}

\begin{figure*}
 \includegraphics[width=2.\columnwidth]{\figpath/pfig5.pdf}%diffcool_img.pdf}
 \caption{A plot of the integrated SiO(2-1) emission from 5 models, 
each using a different method to calculate cooling and all with $\eta$=10.}
\label{fig:coolcmpsio} 
\end{figure*}

@@

\begin{figure*}
 \includegraphics[width=2.\columnwidth]{\figpath/pfig7.pdf}%molcjet_310_molform.pdf}
 \caption{{\it Top}: Number density, n$_{\rm H}$ [cm$^{-3}$], obtained from the reference 
 run along with labels of typical jet features. {\it Bottom}: Dependence of hydrogen fractions on the temperature at two
  points in the flow, viz. the interface of the knot {\it left} with molecular
 medium and at the bow shock {\it right}.}
\label{fig:Hmolform}
\end{figure*}

@@

\begin{figure*}
 \includegraphics[width=2.\columnwidth]{\figpath/pfig10.pdf}%diffabun_img.pdf}%{\figpath/EM_gaussandth.png}
 \caption{Variation of SiO(2-1) emission for runs with molecular
   cooling having different abundance profiles.}
\label{fig:diffabunem}
\end{figure*}

@@

\begin{figure*}
 \includegraphics[width=2.\columnwidth]{\figpath/pfig11.pdf}%diffabun_PV.pdf}%{\figpath/PV_gaussandth.png}
 \caption{Position-velocity maps of SiO(2-1) for the internal
   knots produced in the model with reference parameters and different abundance
   profiles. The contours mark different levels of emission in Kelvins, viz.,
   0.1,0.2,0.6,1.0,1.4,1.8,2.0,3.0,4.0.}
\label{fig:pvdiffabun}
\end{figure*}

@@

\begin{figure*}
 \includegraphics[width=2.\columnwidth]{\figpath/pfig12.pdf}%almamaps_new.pdf}%{\figpath/ALMAmaps3.png}
 \caption{{\bf Left:} The integrated intensity map of SiO(2-1), (5-4)
   and (8-7). The emission map shows the J=5-4 line intensity (in units
   of Jy$\,$kms$^{-1}$/beam), the blue contours show the J=8-7 line
   intensity and the green contours show the J=2-1 line intensity. The
   jet is inclined at an angle of 60$^{\circ}${\bf Right:} The PV
   diagram taken along the axis of the jet for the 5-4 line (in units
   of Jy/beam), showing the higher J transitions highlighting the
   knots of the jet and broad emission at the bow shock. 
   In both panels the ticks on the color bar represent the different contour levels.}
\label{fig:almafig}
\end{figure*}

@@

\begin{figure*}
 \includegraphics[width=2.\columnwidth]{\figpath/pfig14.pdf}%singledish_new.pdf}%{\figpath/LineRatio_THDeq1.png}
 \caption{{\em{Top}}: Line profiles in SiO (2-1), (5-4) and (8-7) at one
   the inner knots for the reference molecular cooling run. The profiles are
   obtained when the angle of inclination is 60$^{\circ}$ with respect
 to line of sight. {\em{Bottom left}}: Line intensity ratios SiO(8-7)/(5-4)
and SiO(5-4)/(2-1), as a function of velocity. {\em{Bottom right}}:
Variation of normalised integrated intensity with upper line transition J$_{\rm
  up}$ for the reference run.}
\label{fig:lineratio}
\end{figure*}

>>>>

\begin{figure*}
 \includegraphics[width=2.\columnwidth]{\figpath/pfig4.pdf}%{\figpath/diffcool_sim.pdf}
 \caption{Logarithmic values of jet volume density in units of
   cm$^{-3}$ obtained from dynamical simulations for different cooling
   modes (labelled on the top of each panel) with
   $\eta$ = 10.}
\label{fig:coolcmpdyn}
\end{figure*}

\begin{figure*}
 \includegraphics[width=2.\columnwidth]{\figpath/pfig5.pdf}%diffcool_img.pdf}
 \caption{A plot of the integrated SiO(2-1) emission from 5 models, 
each using a different method to calculate cooling (labelled on the
top of each panel) and all with $\eta$=10.}
\label{fig:coolcmpsio} 
\end{figure*}

@@

\begin{figure*}
 \includegraphics[width=2.\columnwidth]{\figpath/pfig7.pdf}%molcjet_310_molform.pdf}
 \caption{{\it Top}: Logarithmic values of total hydrogen number density, n$_{\rm H}$),
   in units of cm$^{-3}$, obtained from the reference 
 run along with labels of typical jet features. {\it Bottom}: Dependence of hydrogen fractions on the temperature at two
  points in the flow, viz. at the interface of the knot ({\it left}) with molecular
 medium and at the bow shock ({\it right}).}
\label{fig:Hmolform}
\end{figure*}

@@

\begin{figure*}
 \includegraphics[width=2.\columnwidth]{\figpath/pfig10.pdf}%diffabun_img.pdf}%{\figpath/EM_gaussandth.png}
 \caption{Integrated intensity maps of SiO(2-1) line in units of K, for runs with molecular
   cooling and having different abundance profiles.}
\label{fig:diffabunem}
\end{figure*}

@@

\begin{figure*}
 \includegraphics[width=2.\columnwidth]{\figpath/pfig11.pdf}%diffabun_PV.pdf}%{\figpath/PV_gaussandth.png}
 \caption{Position-velocity maps of SiO(2-1) for the internal
   knots produced in the model with reference parameters and different abundance
   profiles. The contours mark different levels of emission in K, viz.,
   0.1,0.2,0.6,1.0,1.4,1.8,2.0,3.0,4.0.}
\label{fig:pvdiffabun}
\end{figure*}

@@

\begin{figure*}
 \includegraphics[width=2.\columnwidth]{\figpath/pfig12.pdf}%almamaps_new.pdf}%{\figpath/ALMAmaps3.png}
 \caption{{\bf Left:} The integrated intensity map of SiO(2-1), (5-4)
   and (8-7). The emission map shows the J=5-4 line intensity (in units
   of Jy$\,$kms$^{-1}$/beam), the blue contours show the J=8-7 line
   intensity and the green contours show the J=2-1 line intensity. The
   jet is inclined at an angle of 60$^{\circ}$. {\bf Right:} The PV
   diagram taken along the axis of the jet for the 5-4 line (in units
   of Jy/beam), showing the higher J transitions highlighting the
   knots of the jet and broad emission at the bow shock. 
   In both panels the ticks on the color bar represent the different contour levels.}
\label{fig:almafig}
\end{figure*}

@@

\begin{figure*}
 \includegraphics[width=2.\columnwidth]{\figpath/pfig14.pdf}%singledish_new.pdf}%{\figpath/LineRatio_THDeq1.png}
 \caption{{\em{Top}}: Line profiles in SiO (2-1), (5-4) and (8-7) at one
   of the inner knots for the reference molecular cooling run. The profiles are
   obtained when the angle of inclination is 60$^{\circ}$ with respect
 to line of sight. {\em{Bottom left}}: Line intensity ratios SiO(8-7)/(5-4)
and SiO(5-4)/(2-1), as a function of velocity. {\em{Bottom right}}:
Variation of normalised integrated intensity with upper line transition J$_{\rm
  up}$ for the reference run.}
\label{fig:lineratio}
\end{figure*}
